\PYGEOMETRY{}: a Python library for the creation of Monte Carlo radiation transport physical geometries

### 2020-09-16 public/paper/pyg4ometry.tex
avoid stunted and overly terse english
full stop at end of eqn as they're technically part of the prose
also add some words before the equation so  it flows

\begin{figure}[htb!]
\begin{center}
\includegraphics[width=5cm]{./diagrams/lvToPv.pdf}
\caption{Placement of physical volume inside a logical volume.}
\label{fig:lvToPv}
\end{center}
\end{figure}

The transformation  $\mathbf{M}$  and translation $\mathbf{T}$ from mother to daugher is 
\begin{eqnarray}
\mathbf{M} 	& = &  \mathbf{S}_d  \mathbf{R}_d \\
\mathbf{T} 	& = &  \mathbf{T}_d
\end{eqnarray}
%
If the mother volume is placed in the world then the placement transformation $\mathbf{M}_w$ and translation $\mathbf{T}_w$ 
\begin{eqnarray}
\mathbf{M}_w	  	& = & \mathbf{M}_m \mathbf{M}_d  = \mathbf{S}_m \mathbf{R}_m  \mathbf{S}_d \mathbf{R}_d				\label{eqn:worldToDaughter1}\\
\mathbf{T}	_w 		& = & \mathbf{M}_m \mathbf{T}_d + \mathbf{T}_m= \mathbf{S}_m \mathbf{R}_m \mathbf{T}_d + \mathbf{T}_m  \label{eqn:worldToDaughter2}
\end{eqnarray}
where the subscript $m$ indicates mother volume and $d$ indicates daughter volume. Given a hierarchy of logical and physical volumes, 
Equations~\ref{eqn:worldToDaughter1} and \ref{eqn:worldToDaughter2} can be used recursively to place an arbitrary number of nested volumes.

>>>>

\begin{figure}[htb!]
\begin{center}
\includegraphics[width=5cm]{./diagrams/lvToPv.pdf}
\caption{The placement of a physical volume inside a logical volume.}
\label{fig:lvToPv}
\end{center}
\end{figure}

The transformation  $\mathbf{M}$  and translation $\mathbf{T}$ from mother to daugher is 
\begin{eqnarray}
\mathbf{M} 	& = &  \mathbf{S}_d  \mathbf{R}_d\,, \\
\mathbf{T} 	& = &  \mathbf{T}_d\,.
\end{eqnarray}
%
If the mother volume is placed in the world then the placement transformation $\mathbf{M}_w$ and translation $\mathbf{T}_w$ are expressed as
\begin{eqnarray}
\mathbf{M}_w	  	& = & \mathbf{M}_m \mathbf{M}_d  = \mathbf{S}_m \mathbf{R}_m  \mathbf{S}_d \mathbf{R}_d\, ,				\label{eqn:worldToDaughter1}\\
\mathbf{T}	_w 		& = & \mathbf{M}_m \mathbf{T}_d + \mathbf{T}_m= \mathbf{S}_m \mathbf{R}_m \mathbf{T}_d + \mathbf{T}_m\,,  \label{eqn:worldToDaughter2}
\end{eqnarray}
where the subscript $m$ indicates mother volume and $d$ indicates daughter volume. Given a hierarchy of logical and physical volumes, 
Equations~\ref{eqn:worldToDaughter1} and \ref{eqn:worldToDaughter2} can be used recursively to place an arbitrary number of nested volumes.
